Estimating duration in the presence of misclassification

### 2024-03-26 biology-data.tex
Clarify size of immune response

A host's \emph{viral load}, the quantity of viral particles in a host, is the underlying biological process driving the different periods and characteristics of an infection~\autocite{puhachSARSCoV2}.
Any host's viral load is determined by the interaction of many biological processes, most prominently the virus's replication increasing the viral load and the host's immune response reducing the viral load~\autocite{keVivo}.
Viral replication requires the virus to infect a host cell and then use the host cell's machinery to produce more virus; as more host cells are infected this process slows because there are fewer remaining potential host cells, known as \emph{target cells}, to infect.
The rate at which host cells are infected slows over time because there are fewer remaining target cells to infect.
The host's immune system can slow this process by various mechanisms; the most relevant for SARS-CoV-2 is by making some target cells less susceptible to infection.
A host's immune response is triggered by the viral load and becomes stronger as the viral load increases.
A high viral load is associated with being more infectious, more likely to test positive on an RT-PCR test, and the start of symptoms~\autocite{puhachSARSCoV2,keVivo}.

>>>>

A host's \emph{viral load}, the quantity of viral particles in a host, is the underlying biological process driving the different periods and characteristics of an infection~\autocite{puhachSARSCoV2}.
Any host's viral load is determined by the interaction of many biological processes, most prominently the virus's replication increasing the viral load and the host's immune response reducing the viral load~\autocite{keVivo}.
Viral replication requires the virus to infect a host cell and then use the host cell's machinery to produce more virus; as more host cells are infected this process slows because there are fewer remaining potential host cells, known as \emph{target cells}, to infect.
The host's immune system can modify this process by various mechanisms; the most relevant for SARS-CoV-2 is by making some target cells temporarily immune from infection.
The immune system response contribution to the reduction in target cells is several orders of magnitude larger than the reduction in target cells due to viral replication.
The rate at which host cells are infected slows over time because there are fewer remaining target cells to infect.
A host's immune response is triggered by the viral load and becomes stronger as the viral load increases.
A high viral load is associated with being more infectious, more likely to test positive on an RT-PCR test, and the start of symptoms~\autocite{puhachSARSCoV2,keVivo}.
